Balsa: A Compact Line Notation Based on SMILES

### 2022-07-19 manuscript.tex
Replaces writing strings with stack graphic with table. Closes #32

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{stack-for-writer.pdf}
    \caption{Stack for writing strings. Traversal of the root atom (C) creates a new entry. Encountering the start of a branch (N, S) creates a new entry preceded by an open parenthesis symbol (\ttt{(}). Extending a branch writes to the top stack item (I, F, O). Closing a branch pops the top item then concatenates it, together with a close parenthesis symbol (\ttt{)}), to the new top item.}
    \label{fig:stack-for-writer}
\end{figure}

>>>>

% \begin{table}
%     \caption{Atomic Attributes.}
%     \centering
%     \begin{tabular}{l L l l}
%         \hline
%         Attribute & Description & Type & Default \\
%         \hline
%         \ttt{element} & Elemental symbol & \ttt{\{Element\}} & \ttt{None} \\
%         \ttt{isotope} & Mass number & \ttt{\{1..1000\}} & \ttt{None} \\
%         \ttt{hydrogens} & Hydrogen count & \ttt{Implicit}, \ttt{0..10} & 0 \\
%         \ttt{charge} & Formal charge & \ttt{-9..10} & 0 \\
%         \ttt{selected} & Selection status & \ttt{?} & \ttt{false} \\
%         \ttt{parity} & Configuration & \ttt{\{AtomParity\}} & \ttt{None} \\
%         \ttt{edges} & Edges directed toward child nodes & \ttt{[Edge]} & \ttt{[]} \\
%         \hline
%     \end{tabular}
%     \label{table:atomic-attributes}
%     \end{table}

\begin{table}
    \caption{Writing a string with the aid of a stack.}
    \centering
    \begin{tabular}{c}
        \includegraphics[width=\columnwidth]{tree-for-stack.pdf}
    \end{tabular}

    \bigskip

    \begin{tabular}{c l l}
        \hline
        Step & Action & Stack \\
        \hline
        1  & root C   & \enquote{C}                             \\
        2  & open     & \enquote{C},\enquote{(}                 \\
        3  & extend N & \enquote{C},\enquote{(N}                \\
        4  & open     & \enquote{C},\enquote{(N},\enquote{(}    \\
        5  & extend S & \enquote{C},\enquote{(N},\enquote{(S}   \\
        6  & extend I & \enquote{C},\enquote{(N},\enquote{(SI}  \\
        7  & close    & \enquote{C},\enquote{(N(SI)}            \\
        8  & extend F & \enquote{C},\enquote{(N(SI)F}           \\
        9  & close    & \enquote{C(NSI)F)}                      \\
        10 & extend O & \enquote{C(NSI)F)O}                     \\
        \hline
    \end{tabular}
    \label{table:stack-for-writing-string}
\end{table}
